On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Cosmetics edits to the intro

How do we characterize an integral point set?
For example, we can count the number of points in it, which is always finite~\cite{anning1945integral,erdos1945integral}
and is further called the cardinality;
alternatively, we can naturally% TODO: naturally/essentially? cf. arxiv/1
define the diameter of a finite point set.

\begin{dfn}
	A diameter of the integral point set $\mathcal{P}$ is defined as
	\begin{equation}
		\operatorname{diam(\mathcal{P})} = \underset{P_{1}, P_{2} \in
		\mathcal{P}}{\max} |P_{1}P_{2}|
	\end{equation}
\end{dfn}

Every integral point set also has a characteristic~\cite{kemnitz1988punktmengen,kurz2005characteristic}.

>>>>

How do we describe an integral point set?
For example, with the number of points in it, which is always finite~\cite{anning1945integral,erdos1945integral}
and is said to be the \emph{cardinality} of the IPS.
Furthermore, we can naturally % TODO: naturally/essentially? cf. arxiv/1
define the diameter of a finite point set.

\begin{dfn}
	The diameter of the integral point set $\mathcal{P}$ is defined as
	\begin{equation}
		\operatorname{diam(\mathcal{P})} = \underset{P_{1}, P_{2} \in
		\mathcal{P}}{\max} |P_{1}P_{2}|
	\end{equation}
\end{dfn}

Every integral point set also has a characteristic~\cite{kemnitz1988punktmengen,kurz2005characteristic}.
Characteristic of an IPS does not change if the set is moved, dilated ot flipped;
moreover, even addition or deletion of a point does not change the characteristic of IPS.
